Copyright

### 2025-07-09 copyright.qmd
Cite and attribute educational video

The following video "The correct indication of a license"
embedded from the TIB AV-Portal ([Data Privacy Statement](https://av.tib.eu/privacy))
explains the correct attribution of works under Creative Commons licenses.

```{=html}
<details>
  <summary>Load video</summary>
  <div style="position: relative; width: 100%; aspect-ratio: 16 / 9;">
    <iframe loading="lazy" src="https://av.tib.eu/player/53550" allowfullscreen style="position: absolute; top: 0; left: 0; width: 100%; height: 100%;"></iframe>
  </div>
</details>
```
:::

>>>>

The following video by @Brinken2021
embedded from the TIB AV-Portal ([Data Privacy Statement](https://av.tib.eu/privacy))
explains the correct attribution of works under Creative Commons licenses.

```{=html}
<details>
  <summary>Load video</summary>
  <p><div style="position: relative; width: 100%; aspect-ratio: 16 / 9;">
    <iframe loading="lazy" src="https://av.tib.eu/player/53550" allowfullscreen style="position: absolute; top: 0; left: 0; width: 100%; height: 100%;"></iframe>
  </div></p>
  <p>The video “The correct indication of a license: Aspects to consider when reusing the work of others” by Helene Brinken, Jonas Hauss, and Jessika Rücknagel is licensed under <a href="https://creativecommons.org/licenses/by/3.0/de/deed.de">CC&nbsp;BY&nbsp;3.0&nbsp;DE</a>.</p>
</details>
```
:::
